\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-18 k-planar.tex
added comments

\note{DW}{This subsection needs a clean-up; define $(g,d)$-framed graph. Is the following lemma known (at least in the $g=0$ case)?}
\note{PM}{I have no idea if this is known.  If so, it's probably not stated in terms of frames.}
\begin{lem}
\label{MewMapGraphLemma}
For all integers $g\geq 0$ and $d\geq 3$, every $(g,d)$-map graph is a spanning subgraph of a $(g,d)$-framed graph.
\end{lem}

>>>>

\note{DW}{This subsection needs a clean-up; define $(g,d)$-framed graph. Is the following lemma known (at least in the $g=0$ case)?} \note{PM}{I have no idea if this is known.  If so, it's probably not stated in terms of frames.} \note{DW}{I will work this out. We should mention \citet{Brandenburg19,Brandenburg20}. \citet{Brandenburg20} also uses multigraphs, and this paper also mentions 1-planar graphs. So I suspect \cref{1_planar_is_4_framed} is known. I need to go now.}

\begin{lem}
\label{MewMapGraphLemma}
For all integers $g\geq 0$ and $d\geq 3$, every $(g,d)$-map graph is a spanning subgraph of a $(g,d)$-framed graph.
\end{lem}
